Accessing the nucleon transverse structure in inclusive deep inelastic scattering

### 2017-06-01 1607 - JMC for g2/Paper/JMC_dis.tex
minor changes
Checked a few misprints here and there. Changed a few sentences, with
no deep change of meaning. Still have to check Eqs. 25-26.

\begin{abstract}
We revisit the standard analysis of inclusive Deep Inelastic Scattering
off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons -  a process that can be described in terms of suitable "jet" correlators. As a consequence, a spin-flip term
associated with the invariant mass of the produced hadrons is generated
non perturbatively and couples to the target's transversity distribution
function. In inclusive cross sections, this provides an hitherto neglected and
large contribution to the twist-3 part of the $g_2$ structure function, that
can explain the discrepancy between recent calculations and fits of this
quantity.  It also provides an extension of the Burkhardt--Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
%Perspectives to measure the new spin-flip term, and applications to
%spin-1 targets will be briefly discussed. 
\end{abstract}

@@

The tensor charge is a fundamental property of the nucleon, that is at
present poorly constrained but of fundamental importance, not the least because its knowledge can also be used to put constraints on searches for physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
The tensor charge has been estimated in lattice QCD (see, \eg,
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn}), but
only limited information is available from direct measurements. Its experimental extraction requires first of all flavor-separated measurements of the so-called transversity parton distribution function,
denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review and
Refs.~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa} for the most recent
extractions). Secondly, one needs to perform flavor-by-flavor integrals of these, that correspond to the contribution of a parton flavor $q$ to the tensor charge.

@@

In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
We revisit the standard analysis of the DIS handbag diagram, taking into account the fact that on-shell quarks cannot, in fact, be present in the final state, but they rather decay and form mini-jets of hadrons. This is sufficient to modify the structure of the DIS
cut diagram, even if none of the hadrons is detected in the final
state. For a proper description of this effect, we include ``jet
correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant.

The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a non perturbative mass of order 100 MeV, much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes. Here, we formalize this idea in the context of collinear factorization, and observe that jet correlators introduce a new
contribution already in one-photon exchange processes, and more precisely to the inclusive $g_2$ structure function. The new term is proportional to the transversity distribution function multiplied by a new nonperturbative ``jet mass'', which will be precisely defined below, and has the interesting features that:
(a) it violates the Wandzura--Wilczek relation;
(b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
(c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
We Estimates this new jet-mass-induced contribution based on a recent extraction of the transversity distribution, and show it can indeed be very large.

@@

The correlator $\Xi$ can be parametrized in terms of jet parton correlation
functions $A_i$ and $B_i$ through a Lorentz covariant Dirac decomposition that utilizes the vectors $l$ and $n_+$, 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ ,
\label{e:jetexpansion}
\end{equation} 
where $\Lambda$ is an arbitrary scale, introduced for power counting purposes.
In this parametrization, no terms proportional to $\gamma_5$ enter because of parity invariance. Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order and will not be considered further in this paper. We focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
    + O(\Lambda^2/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the cut quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one (or, in other words, the interacting rather than the free quark fields).
The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral
representation of the cut quark propagator (see, e.g., Sec.~6.3 of
\cite{D'Hoker:2004aa} and Sec.~2.7.2 of \cite{Romao:2013aa}),
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu\,\id + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -\mu^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ can be interpreted as the invariant mass of the current jet, {\it
  i.e.}, of the particles going through the cut in the top blob of
Fig.\ref{fig:handbags}(a). The $J_i$ are the spectral functions of the
quark propagator, also called ``jet functions'' in
\cite{Accardi:2008ne}, and can be interpreted as current-jet mass distributions. As a consequence of positivity constraints and CPT invariance, These satisfy \cite{D'Hoker:2004aa,Romao:2013aa,Weinberg:1995mt}
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

@@

When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order $O(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}. In this paper, where we limit our
attention to effects of order $O(1/Q)$, we can neglect $k^-$ compared to $q^-$. As a consequence, we can extend the integration over $dl^2$ to infinity, with the consequence that the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator 
\begin{equation} 
  \Xi(l^-,{\bm l_T}) \equiv \int \frac{dl^2}{2l^-} \, \Xi(l) 
    =  \frac{\Lambda}{2 l^-}\,\xi_1 \id
    +  \xi_2 \frac{\nslash_-}{2} 
    + O(l_T/l^-) + \text{higher\ twists} \ .
\end{equation} 
The neglected ${\bm l_T}$-dependent and higher twist terms only contribute to $O(1/Q^2)$ to the inclusive cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we obtain
\begin{align}
\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
       \equiv \frac{\mj}{\Lambda},
&
\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ ,
\end{align} 
where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
It is important to notice that while $\xi_2=1$ exactly due to CPT invariance
(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of the spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$ with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore estimate 
\begin{align}
  \label{eq:mjet}
  \mj = O(100 \text{\ MeV}) \ .
\end{align}
Although $\mj$ is in general a nonperturbative quantity, it is interesting to
notice that on the perturbative vacuum, 
\begin{align*}
  \Xi^\text{pert}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + O(\alpha_s) \ ,
\end{align*}
where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
% \begin{align}
%   \label{eq:xi2_chiral_cond}
%   \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
%    = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
% \end{align}
% % \todo{[AA] 2 issues here: (1) possible factors of 4. 
% % (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.} 
% On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
% Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
% $\mj = \,_{\text{pert}} \langle 0
% |  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
However, we are here considering non perturbative effects
in the quark propagation, and $\mj \gg \mq$. 
Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.

@@

In diagram (b), the $\xi_1$ term contributes to $O(1/Q^2)$, so that up to $O(1/Q)$ considered in this paper this give the same contribution as in the conventional handbag calculation. The novel element in our analysis, instead, is the jet's quark-gluon-quark correlator $\Xi_A^{\mu}(l,k)$ in diagram (c), defined as 
\begin{equation} 
\begin{split} 
  \left(\tilde \Xi_A^{\mu} \right)_{ij} &=
   \int \frac{\de^4 \eta}{(2\pi)^{4}}\;
   e^{\ii k \cdot \eta}\,
   \langle 0|\,
   {\cal U}^{n_+}_{(+\infty,\eta)}\,
   g A^{\mu}(\eta)\,
   \,\psi_i(\eta)
   \,\bar{\psi}_j(0)\,
   {\cal U}^{n_+}_{(0,+\infty)}
   |0\rangle \ .
\label{e:xi_A}
\end{split} 
\end{equation}  
This diagram and its Hermitian conjugate are not only important to account for
all contribution of order $O(1/Q)$, but also to restore gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.

Rather than directly using the definition \eqref{e:xi_A}, it is convenient and instructive to calculate the inclusive cross section as an integral of the semi-inclusive one summed over all produced hadron flavors, then utilize the QCD equations of motion, sum over all hadron flavors, and take advantage of  
\begin{align}
  \label{eq:SIDIS_to_DIS}
  \sum_h \int d^2p_{hT}\frac{dp_h^-}{2p_h^-} \,p_h^- \, \Delta^h(l,p_h) = l^-\,\Xi(l) \ , 
\end{align}
where $\Delta^h$ is the quark fragmentation correlator for production of a
hadron of flavor $h$ and momentum $p_h$, discussed in detail  \cite{Bacchetta:2006tn}. In terms of
the TMD fragmentation functions we are interested in, the sum rule \eqref{eq:SIDIS_to_DIS} reads 
\begin{align}
  \label{eq:SIDIS_to_DIS_TMDlevel1}
  \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
  \label{eq:SIDIS_to_DIS_TMDlevel2}
  \sum_h \int dz d^2p_{hT} E^h(z,p_{hT}) & = \xi_1 = \mj / \Lambda\ ,
\end{align}
where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function, that depends on the hadron's collinear momentum fraction $z$ and transverse
momentum $p_{hT}$, and $E^h(z,p_{hT})$ is a chiral-odd twist-3 function
defined in \cite{Bacchetta:2006tn}.

@@

Finally, the contraction of the hadronic tensor with the leptonic tensor leads
to the following result for the inclusive DIS cross section up to order $\Lambda/Q$~\cite{Bacchetta:2006tn}:
\begin{align}
\frac{d\sigma}{d\xbj \, dy\, d\phi_S}
%&
=
\frac{2 \alpha^2}{\xbj y Q^2}\,
\frac{y^2}{2\,(1-\varepsilon)}\, 
\biggl\{
&F_{T} + \varepsilon F_{L}
+ S_\parallel \lambda_e\,
  \sqrt{1-\varepsilon^2}\; 
F_{LL}
%\nonumber 
%\\  &
+ |\bm{S}_\perp| \lambda_e\, \sqrt{2\,\varepsilon (1-\varepsilon)}\, 
  \cos\phi_S\, 
F_{LT}^{\cos \phi_S}
 \biggr\} \ ,
\label{e:crossdis}
\end{align}
where $\phi_S$ is the angle between the transverse component of the proton spin vector and the lepton plane, $\epsilon$ is the ratio of the longitudinal and transverse photon fluxes, and $\lambda_e$ is the electron's helicity. 
The structure functions on the right hand side read
\begin{align}
F_{UU ,T} &= \xbj\,\sum_q e_q^2\,f_1^q(\xbj),
\\
F_{UU ,L} &= 0,
\\
F_{LL} &=\xbj\,\sum_q e_q^2\,g_1^q(\xbj),
\\
F_{UT}^{\sin \phi_S}&=0,
\label{e:FUTint}
\\
F_{LT}^{\cos \phi_S}&=-\xbj\,\sum_q e_q^2\, \frac{2\Lambda}{Q}\,
\biggl(\xbj  g_T^q(\xbj)
   + \frac{\mj -\mq}{\Lambda} \, h_{1}^q(\xbj) \biggr) \ ,
\label{e:FLTint}
\end{align}
where $f_1^q$, $g_1^q$ and $h_1^q$ are the unpolarized, polarized, and transversity PDFs,respectively.
The second term in the last structure function is a new result from our
analysis, and, although proportional to the jet mass, it is not suppressed as an inverse power of $Q$ compared to the
standard $g_T$ term. Perturbatively, $M_q^\text{pert}=m_q$ and the new term vanishes. However, on the nonperturbative vacuum the jet mass $M_q$ is much larger than the quark's current mass $m_q$, originating a nonnegligible term to the twist-3 part of the target's $g_2$ structure function, as we will discuss in the next section.

@@

The new term in Eq.\eqref{e:FLTint} only appears in the $g_2=\frac12 \sum_q e_q^2(g_T^q-g_1^q)$ structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
\begin{align}
\label{e:g2}
  g_2(\xbj) = g_2^{WW}(\xbj) + \frac{1}{2}\,\sum_a e_a^2
\biggl(
    \widetilde g_T^{a \star}(\xbj) 
    + \int_\xbj^1\frac{dy}{y} \widehat{g}_T^q(y) 
    + \frac{\mq}{\Lambda} \left(\frac{h_1^q}{x}\right)^\star(\xbj) 
    + \frac{\mj-\mq}{\Lambda} \frac{h_1^q(\xbj)}{\xbj} 
\Biggr) \ ,
\end{align}
where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$, and $\tilde g_T$ and $\hat g_T$ are pure twist-3 functions defined in that reference. The first four terms coincide with the result obtained in the conventional handbag
approximation \cite{Accardi:2009au}, while the fifth is new. Note that even if
the relation is written for the sum over quark flavors weighted by their charge
squared, it is also valid flavor by flavor; in fact, the steps
leading to such a decomposition are formulated at the quark correlator level.

The first term is also known as the Wandzura-Wilczek function, $g_2^{WW} =
-g_1^*$, with $g_1=\frac12 \sum_q e_q^2 g_1^q$, and contains all the twist-2 chiral-even contributions to the $g_2$ structure coming from quark-quark correlators. The second and third
terms contain all ``pure twist-3'' contributions, i.e., those coming from
quark-gluon-quark correlators. The fourth and fifth terms contain chiral-odd twist-2 contributions and depend on the
transversity distribution function, $h_1$. 
The fourth term is usually neglected for
light quarks since it is proportional to $\mq=O$(1 MeV). The last term,
new in our analysis, is again proportional to the transversity distribution but multiplied by the jet mass $\mj=O$(100 MeV), so that it cannot be a priori neglected.

>>>>

\begin{abstract}
We revisit the standard analysis of inclusive Deep Inelastic Scattering
off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons --  a process that can be described in terms of suitable ``jet'' correlators. As a consequence, a spin-flip term
associated with the invariant mass of the produced hadrons is generated
non perturbatively and couples to the target's transversity distribution
function. In inclusive cross sections, this provides an hitherto neglected and
large contribution to the twist-3 part of the $g_2$ structure function, that
can explain the discrepancy between recent calculations and fits of this
quantity.  It also provides an extension of the Burkhardt--Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
%Perspectives to measure the new spin-flip term, and applications to
%spin-1 targets will be briefly discussed. 
\end{abstract}

@@

The tensor charge is a fundamental property of the nucleon that is at
present poorly constrained but of fundamental importance, not the least because its knowledge can also be used to put constraints on searches for physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
The tensor charge has been estimated in lattice QCD (see, \eg,
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn}), but
only limited information is available from direct measurements. Its experimental extraction requires first of all flavor-separated measurements of the so-called transversity parton distribution function,
denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review and
Refs.~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa} for the most recent
extractions). Secondly, one needs to perform flavor-by-flavor integrals of these, that correspond to the contribution of a parton flavor $q$ to the tensor charge.

@@

In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
We revisit the standard analysis of the DIS handbag diagram, taking into account the fact that on-shell quarks cannot, in fact, be present in the final state, but they rather decay and form jets of hadrons. This is sufficient to modify the structure of the DIS
cut diagram, even if none of the hadrons is detected in the final
state. For a proper description of this effect, we include ``jet
correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant.

The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a non perturbative mass of order 100 MeV, much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes. Here, we formalize this idea in the context of collinear factorization, and observe that jet correlators introduce a new
contribution already in one-photon exchange processes, and more precisely to the inclusive $g_2$ structure function. The new term is proportional to the transversity distribution function multiplied by a new nonperturbative ``jet mass'', which will be precisely defined below, and has the interesting features that:
(a) it violates the Wandzura--Wilczek relation;
(b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
(c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
We estimate this new jet-mass-induced contribution based on a recent extraction of the transversity distribution, and show it can indeed be very large.

@@

The correlator $\Xi$ can be parametrized in terms of jet parton correlation
functions $A_i$ and $B_i$ through a Lorentz covariant Dirac decomposition that utilizes the vectors $l$ and $n_+$, 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ ,
\label{e:jetexpansion}
\end{equation} 
where $\Lambda$ is an arbitrary scale, introduced for power counting purposes.
In this parametrization, no terms proportional to $\gamma_5$ enter because of parity invariance. Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order and will not be considered further in this paper. We focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
    + {\cal O}(\Lambda^2/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the cut quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one (or, in other words, the interacting rather than the free quark fields).
The $A_1$ and $A_2$ terms can be interpreted in terms of the spectral
representation of the cut quark propagator (see, e.g., Sec.~6.3 of
\cite{D'Hoker:2004aa} and Sec.~2.7.2 of \cite{Romao:2013aa}),
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu\,\id + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -\mu^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ can be interpreted as the invariant mass of the current jet, {\it
  i.e.}, of the particles going through the cut in the top blob of
Fig.\ref{fig:handbags}(a). The $J_i$ are the spectral functions of the
quark propagator, also called ``jet functions'' in
\cite{Accardi:2008ne}, and can be interpreted as current-jet mass distributions. As a consequence of positivity constraints and CPT invariance, These satisfy \cite{D'Hoker:2004aa,Romao:2013aa,Weinberg:1995mt}
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqs.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

@@

When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order ${\cal O}(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}. In this paper, where we limit our
attention to effects of order ${\cal O}(1/Q)$, we can neglect $k^-$ compared to $q^-$. As a consequence, we can extend the integration over $dl^2$ to infinity, with the consequence that the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator 
\begin{equation} 
  \Xi(l^-,{\bm l_T}) \equiv \int \frac{dl^2}{2l^-} \, \Xi(l) 
    =  \frac{\Lambda}{2 l^-}\,\xi_1 \id
    +  \xi_2 \frac{\nslash_-}{2} 
    + {\cal O}(l_T/l^-) + \text{higher\ twists} \ .
\end{equation} 
The neglected ${\bm l_T}$-dependent and higher twist terms only contribute to ${\cal O}(1/Q^2)$ to the inclusive cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we obtain
\begin{align}
\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
       \equiv \frac{\mj}{\Lambda},
&
\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ ,
\end{align} 
where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
It is important to notice that while $\xi_2=1$ exactly due to CPT invariance
(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of the spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$ with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore estimate 
\begin{align}
  \label{eq:mjet}
  \mj = {\cal O}(100 \text{\ MeV}) \ .
\end{align}
Although $\mj$ is in general a nonperturbative quantity, it is interesting to
notice that on the perturbative vacuum, 
\begin{align*}
  \Xi^\text{pert}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + {\cal O}(\alpha_s) \ ,
\end{align*}
where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
% \begin{align}
%   \label{eq:xi2_chiral_cond}
%   \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
%    = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
% \end{align}
% % \todo{[AA] 2 issues here: (1) possible factors of 4. 
% % (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.} 
% On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
% Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
% $\mj = \,_{\text{pert}} \langle 0
% |  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
However, we are here considering non perturbative effects
in the quark propagation, and $\mj \gg \mq$. 
Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.

@@

In diagram (b), the $\xi_1$ term contributes to ${\cal O}(1/Q^2)$, so that up to ${\cal O}(1/Q)$ considered in this paper this give the same contribution as in the conventional handbag calculation. The novel element in our analysis, instead, is the jet's quark-gluon-quark correlator $\Xi_A^{\mu}(l,k)$ in diagram (c), defined as 
\begin{equation} 
\begin{split} 
  \left(\tilde \Xi_A^{\mu} \right)_{ij} &=
   \int \frac{\de^4 \eta}{(2\pi)^{4}}\;
   e^{\ii k \cdot \eta}\,
   \langle 0|\,
   {\cal U}^{n_+}_{(+\infty,\eta)}\,
   g A^{\mu}(\eta)\,
   \,\psi_i(\eta)
   \,\bar{\psi}_j(0)\,
   {\cal U}^{n_+}_{(0,+\infty)}
   |0\rangle \ .
\label{e:xi_A}
\end{split} 
\end{equation}  
This diagram and its Hermitian conjugate are not only important to account for
all contribution of order ${\cal O}(1/Q)$, but also to restore gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.

Rather than directly using the definition \eqref{e:xi_A}, it is convenient and instructive to calculate the inclusive cross section as an integral of the semi-inclusive one summed over all produced hadron flavors, then utilize the QCD equations of motion, sum over all hadron flavors, and take advantage of  
\begin{align}
  \label{eq:SIDIS_to_DIS}
  \sum_h \int d^2p_{hT}\frac{dp_h^-}{2p_h^-} \,p_h^- \, \Delta^h(l,p_h) = l^-\,\Xi(l) \ , 
\end{align}
where $\Delta^h$ is the quark fragmentation correlator for production of a
hadron of flavor $h$ and momentum $p_h$, discussed in detail in Ref.~\cite{Bacchetta:2006tn}. In terms of
the TMD fragmentation functions we are interested in, the sum rule \eqref{eq:SIDIS_to_DIS} reads 
\begin{align}
  \label{eq:SIDIS_to_DIS_TMDlevel1}
  \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
  \label{eq:SIDIS_to_DIS_TMDlevel2}
  \sum_h \int dz d^2p_{hT} E^h(z,p_{hT}) & = \xi_1 = \mj / \Lambda\ ,
\end{align}
where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function, that depends on the hadron's collinear momentum fraction $z$ and transverse
momentum $p_{hT}$, and $E^h(z,p_{hT})$ is a chiral-odd twist-3 function
defined in \cite{Bacchetta:2006tn}.

@@

Finally, the contraction of the hadronic tensor with the leptonic tensor leads
to the following result for the inclusive DIS cross section up to order $\Lambda/Q$~\cite{Bacchetta:2006tn}:
\begin{align}
\frac{d\sigma}{d\xbj \, dy\, d\phi_S}
%&
=
\frac{2 \alpha^2}{\xbj y Q^2}\,
\frac{y^2}{2\,(1-\varepsilon)}\, 
\biggl\{
&F_{T} + \varepsilon F_{L}
+ S_\parallel \lambda_e\,
  \sqrt{1-\varepsilon^2}\; 
F_{LL}
%\nonumber 
%\\  &
+ |\bm{S}_\perp| \lambda_e\, \sqrt{2\,\varepsilon (1-\varepsilon)}\, 
  \cos\phi_S\, 
F_{LT}^{\cos \phi_S}
 \biggr\} \ ,
\label{e:crossdis}
\end{align}
where $\phi_S$ is the angle between the transverse component of the proton spin vector and the lepton plane, $\epsilon$ is the ratio of the longitudinal and transverse photon fluxes, and $\lambda_e$ is the electron's helicity. 
The structure functions on the right hand side read
\begin{align}
F_{UU ,T} &= \xbj\,\sum_q e_q^2\,f_1^q(\xbj),
\\
F_{UU ,L} &= 0,
\\
F_{LL} &=\xbj\,\sum_q e_q^2\,g_1^q(\xbj),
\label{e:FLLint}
\\
F_{UT}^{\sin \phi_S}&=0,
\label{e:FUTint}
\\
F_{LT}^{\cos \phi_S}&=-\xbj\,\sum_q e_q^2\, \frac{2\Lambda}{Q}\,
\biggl(\xbj  g_T^q(\xbj)
   + \frac{\mj -\mq}{\Lambda} \, h_{1}^q(\xbj) \biggr) \ ,
\label{e:FLTint}
\end{align}
where $f_1^q$, $g_1^q$ and $h_1^q$ are the unpolarized, polarized, and transversity PDFs,respectively.
The second term in the last structure function is a new result from our
analysis, it is proportional to the jet mass, and it is not suppressed as an
inverse power of $Q$ compared to the 
standard $g_T$ term. Perturbatively, $M_q^\text{pert}=m_q$ and the new term vanishes. However, on the nonperturbative vacuum the jet mass $M_q$ is much larger than the quark's current mass $m_q$, originating a nonnegligible term to the twist-3 part of the target's $g_2$ structure function, as we will discuss in the next section.

@@

The structure functions in Eqs.~\eqref{e:FLLint} -- \eqref{e:FLTint} can be
related to the usual
structure functions $g_1$ and $g_2$ defined. In
particular, the expression of the structure function $g_2$ is
\begin{equation} 
g_2=\frac12 \sum_q e_q^2(g_T^q-g_1^q)
\end{equation}
structure function. Following the derivation in Ref.~\cite{Accardi:2009au}, one finds
\begin{align}
\label{e:g2}
  g_2(\xbj) = g_2^{WW}(\xbj) + \frac{1}{2}\,\sum_a e_a^2
\biggl(
    \widetilde g_T^{a \star}(\xbj) 
    + \int_\xbj^1\frac{dy}{y} \widehat{g}_T^q(y) 
    + \frac{\mq}{\Lambda} \left(\frac{h_1^q}{x}\right)^\star(\xbj) 
    + \frac{\mj-\mq}{\Lambda} \frac{h_1^q(\xbj)}{\xbj} 
\Biggr) \ ,
\end{align}
where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$, and $\tilde g_T$ and $\hat g_T$ are pure twist-3 functions defined in that reference. The first four terms coincide with the result obtained in the conventional handbag
approximation \cite{Accardi:2009au}, while the last is new. Note that even if
the relation is written for the sum over quark flavors weighted by their charge
squared, it is also valid flavor by flavor; in fact, the steps
leading to such a decomposition are formulated at the quark correlator level.

The first term is also known as the Wandzura-Wilczek function, $g_2^{WW} =
-g_1^*$, with $g_1=\frac12 \sum_q e_q^2 g_1^q$, and contains all the twist-2 chiral-even contributions to the $g_2$ structure coming from quark-quark correlators. The second and third
terms contain all ``pure twist-3'' contributions, i.e., those coming from
quark-gluon-quark correlators. The fourth and fifth terms contain chiral-odd twist-2 contributions and depend on the
transversity distribution function, $h_1$. 
The fourth term is usually neglected for
light quarks since it is proportional to $\mq={\cal O}$(1 MeV). The last term,
new in our analysis, is again proportional to the transversity distribution
but multiplied by the jet mass $\mj={\cal O}$(100 MeV), so that it cannot be a priori neglected.
